Multi-Instance Methods for Partially Supervised Image Segmentation

### 2013-08-29 partial_supervision/paper.tex
more on algorithms for structured learning, but broke the algorithm listings?
FIX put chapter commands in separate files, so that the text is not on a new page...

@@

We normalize the kernel $k_{MI}$ \citep{gaertner2002multi} using
\begin{equation}
k(X,X') := \frac{k_{MI}(X,X')}{\sqrt{k_{MI}(X,X)k_{MI}(X',X')}}.
\end{equation}
Training an SVM with this kernel produces a bag-level classifier for each
class, which we will refer to as MIK.  This procedure is very efficient since
the resulting kernel matrix is of size number of bags, which is much smaller
than a kernel matrix of size number of instances, as is commonly used in the
literature~\citep{andrews2003support,nguyen2010new,zhang2008m3miml}.  Another
advantage over other methods is, that it uses a single convex optimization,
whereas other approaches often use iterative
algorithms~\citep{andrews2003support} or need to fit complex probabilistic
models~\citep{zha2008joint}.

>>>>

\chapter{Weakly Supervised Object segmentation via Multiple Instance Learning}

@@

We normalize the kernel $k_{MI}$ \citep{gaertner2002multi} using
\begin{equation}
k(X,X') := \frac{k_{MI}(X,X')}{\sqrt{k_{MI}(X,X)k_{MI}(X',X')}}.
\end{equation}
Training an SVM with this kernel produces a bag-level classifier for each
class, which we will refer to as MIK\@.  This procedure is very efficient since
the resulting kernel matrix is of size number of bags, which is much smaller
than a kernel matrix of size number of instances, as is commonly used in the
literature~\citep{andrews2003support,nguyen2010new,zhang2008m3miml}.  Another
advantage over other methods is, that it uses a single convex optimization,
whereas other approaches often use iterative
algorithms~\citep{andrews2003support} or need to fit complex probabilistic
models~\citep{zha2008joint}.
